### 2011-08-15 doc/theses/vitasek/diplomka.tex
Thesis: in progress.

\begin{table}
  \centering
  \begin{tabular}{| l | l |}
  \hline
  Machine           & Windows \\
  Input data set    & \texttt{100-500} \\
  Iterations        & 20 \\
  Pool size         & 1 \\
  $\alpha$, $\beta$ & $1$, $1$ \\
  \hline
  \end{tabular}
\end{table}

Our experimental set will contain 500 experimental configurations for each of these two GLPK version. Every configuration will use \jmodule{Glpk} CH set to a time limit from 1 to 49 seconds with increments of 2 (25 settings * 20 iterations = 500 configurations in total). There will be no improvement heuristic. The only data we gather in the GnuPlot file are the final qualities (weights).\\

>>>>

\begin{table}
  \caption{GLPK: native vs. Cygwin summary}
  \label{experiment-glpk-native-vs-cygwin-summary}
  \centering
  \begin{tabular}{| l | l |}
  \hline
  Machine           & Windows \\
  Input data set    & \texttt{100-500} \\
  Iterations        & 20 \\
  Pool size         & 1 \\
  $\alpha$, $\beta$ & $1$, $1$ \\
  \hline
  \end{tabular}
\end{table}

Our experimental set will contain 500 experimental configurations for each of these two GLPK version. Every configuration will use \jmodule{Glpk} CH set to a time limit from 1 to 49 seconds with increments of 2, meaning 25 settings * 20 iterations = 500 configurations in total (pseudocode to be found in \ref{listing-experiment-glpk-native-vs-cygwin}). There will be no improvement heuristic. The only data we gather in the GnuPlot file are the final qualities (weights).

\begin{algorithm}
\caption{GLPK: native vs. Cygwin generation}
\label{listing-experiment-glpk-native-vs-cygwin}
\begin{algorithmic}
\ENSURE experimental set $ES$
\STATE $ES \gets \emptyset$
\FOR{$i = 1 \to 20$}
	\FOR{$time = 1 \to 49 step 2$}
    \STATE $ES \gets IH = $ \jmodule{Glpk} $, limit = time, IH = \emptyset$  
  \ENDFOR
\ENDFOR
\RETURN $ES$
\end{algorithmic}
\end{algorithm}
